\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=20mm,
 }

\title{ECE472-Assignment 3}

\author{Mohannad Al Arifi}

\date{\today}

\linespread{1.3} % 1.5 spacing
\renewcommand{\baselinestretch}{1}

\begin{document}
\maketitle

\begin{itemize}
   \item Brief architecture overview
   \item Optimizing for (code and) data cache
   \begin{enumerate}
      \item General suggestions
      \item Data structures
   \end{enumerate}
   \item Aliasing
\end{itemize}

\subsection{cache review}
\begin{itemize}
   \item ~32/64 bytes cache lines 
   \item N-way set-associative: logical cache line $\rightarrow$ N physical lines. Helps minimize cache line thrashing.
   \item Foes:
   \begin{enumerate}
      \item Compulsory misses: Data read for first time.
      \item Capacity misses: small cache space for all active data. Too much data accessed inbetween successive use.
      \item Conflict misses: cache thrashing because data mapping to same cache lines.
   \end{enumerate}
   \item Friends:
   \begin{enumerate}
      \item Rearrange (code, data): to increase spatial locality.
      \item Reduce (size,\# cache lines read): smarter smaller formats, compression.
      \item Reuse (cache lines): increase temporal and spatial locality.
   \end{enumerate}
   \item pay attention to:
   \begin{enumerate}
      \item Profile
      \item study the generated code
      \item locality
      \item size
   \end{enumerate}

\end{itemize}

\subsection{data cache optimization}
\begin{itemize}
   \item prefetching/preloading data
   \begin{enumerate}
      \item Software prefetching
      \begin{enumerate}
	 \item Not-too-Early
	 \item Not-too-Late
	 \item Greedy
      \end{enumerate}
      \item Hardware prefetching
      \begin{enumerate}
	 \item Hit-under-miss
      \end{enumerate}
   \end{enumerate}
   \item Cache-conscious structure layout
   \begin{enumerate}
	\item Field reordering: e.g. Likely accessed together so store them together.
	\item Hot/cold splitting
	\item Compiler padding: watchout and store in decreasing order. *Good one.
   \end{enumerate}
   \item Cache performance analysis: 
   \begin{enumerate}
	\item Usage patterns:
	    \begin{enumerate}
		\item Activity: hot/cold field
		\item Correlation: for field reordering
	    \end{enumerate}
	\item Logging tool
   \end{enumerate}
   \item Tree data structures
   \begin{enumerate}
	\item Rearrange nodes: increase spatial locality
	\item Reduce size: pointer elimination, compression.
	\item Breadth-first order: requires storage for complete tree of height H
	\item Depth-first order: stores existing nodes.
   \end{enumerate}
   \item Linearization caching
   \begin{enumerate}
      \item linear data: best spatial locality, easily prefetchable.	
      \item So linearize at runtime.
   \end{enumerate}
   \item Memory allocation
   \begin{enumerate}
      \item Allocate from pools not heap. *interesting.
      \item Free ASAP, reuse immediately.
   \end{enumerate}
   \item Aliasing/anti-aliasing
   \begin{enumerate}
      \item Aliasing is multiple references to the same storage location.
      \item Free ASAP, reuse immediately.
      \end{enumerate}
      \item restrict-qualified pointer
      \begin{enumerate}
	 \item Restricting can help perform parallel operations not possible otherwise.
      \end{enumerate}

\end{itemize}

\end{document}
